Through the eyes of the teacher

### 2021-05-20 paper_1/paper_1_supplement_et_aoi.Rmd
update manual AOIs

#### Areas of Interest (GRI)

``` {r AOIs, echo=FALSE} 
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

@@

>>>>

#### DYNAMIC Areas of Interest (AOI)

``` {r dAOIs, echo=FALSE} 
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

@@

#### MANUAL Areas of Interest (AOI)

``` {r mAOIs, echo=FALSE} 
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages('papaja'); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index

# prepare data (selected from AOI data)
et.raw.data<-read.table("./Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)
